
\documentclass[format=acmsmall, review=false, screen=true]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}


\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


% Metadata Information
\acmJournal{TOMM}
%\acmVolume{1}
%\acmNumber{1}
%\acmArticle{1}
%\acmYear{2018}
%\acmMonth{11}
\copyrightyear{2019}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{November 2018}
\received[revised]{2019}
\received[accepted]{2019}


% Document starts
\begin{document}
% Title portion. Note the short title for running heads
\title[RenderGAN]{RenderGAN: enhancing real-time rendering efficiency with Deep Learning}

\author{Marco Mameli}
\orcid{0000-0002-5269-9939}
\affiliation{%
  \institution{Universit\`a Politecnica delle Marche, Dipartimento di Ingegneria dell'Informazione (DII)}
  \streetaddress{Via Brecce Bianche, 12}
  \city{Ancona}
  \state{}
  \postcode{60131}
  \country{Italy}}
\email{m.mameli@pm.univpm.it}

\author{Marina Paolanti}
\affiliation{%
  \institution{University of Macerata, Department of Political Sciences, Communication and International Relations}
  \streetaddress{Via Don Minzoni, 22A}
  \city{Macerata}
  \state{}
  \postcode{62100}
  \country{Italy}
}
\email{marina.paolanti@unimc.it}

\author{Adriano Mancini}
\orcid{0000-0001-5281-9200}
\affiliation{%
  \institution{Universit\`a Politecnica delle Marche, Dipartimento di Ingegneria dell'Informazione (DII)}
  \streetaddress{Via Brecce Bianche, 12}
  \city{Ancona}
  \state{}
  \postcode{60131}
  \country{Italy}
}
\email{a.mancini@univpm.it}

\author{Primo Zingaretti}
\affiliation{%
  \institution{Universit\`a Politecnica delle Marche, Dipartimento di Ingegneria dell'Informazione (DII)}
  \streetaddress{Via Brecce Bianche, 12}
  \city{Ancona}
  \state{}
  \postcode{60131}
  \country{Italy}
}
\email{p.zingaretti@staff.univpm.it}


\begin{abstract}
In the domain of computer graphics, achieving high visual quality in real-time rendering remains a formidable challenge due to the inherent time-quality trade-off. Conventional real-time rendering engines sacrifice visual fidelity for interactive performance, while image generation using path-tracing techniques can be exceedingly time-consuming. In this paper, we introduce RenderGAN, a cutting-edge deep learning-based solution designed to address this critical challenge in real-time rendering. RenderGAN utilizes G-Buffers and information from a real-time rendering engine as inputs to produce output images with exceptional visual fidelity. Its encoder-decoder architecture, trained using the Generative Adversarial Network (GAN) framework with perceptual loss, enhances image realism. To evaluate RenderGAN's effectiveness, we quantitatively compare the generated images with those of a path-tracing engine, obtaining a remarkable Universal Image Quality Index (UIQI) value of 0.898. RenderGAN's open-source nature fosters collaboration, driving advancements in real-time computer graphics and rendering techniques. By bridging the gap between real-time and path-tracing rendering, RenderGAN opens new horizons for accelerated image generation, inspiring innovation and unlocking the full potential of real-time visual experiences.
Project page: https://github.com/marcomameli1992/RenderNet
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003033.10003034.10003035.10003036</concept_id>
       <concept_desc>Networks~Layering</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[300]{Networks~Layering}

%
% End generated code
%
\keywords{Computer Graphics, Deep Learning, Generative Adversarial Networks, RenderGAN}




\maketitle

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{M. Mameli et al.}

\input{main}


\end{document}